Energy and the CES production function

### 2015-10-16 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Added sigma_1 and sigma to naturalCoeffs.

  modelsCSP <- list()
  # Output elasticities based on cost share theorem
  alphaCSP <- 0.3 # Fraction of national accounts spent on capital
  betaCSP <- 0.7 # Fraction of national accounts spent on labor
  for (country in countries){
    for (adj in c("unadjusted", "adjusted")){
      # Replace with better code later. 
      # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
      # or something like that.
      form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
      yVar <- as.name(summands(form, n=1, right=FALSE))
      kVar <- as.name(summands(form, n=1))
      lVar <- as.name(summands(form, n=2))
      tVar <- as.name(summands(form, n=3))
      data <- historicalData[[country]]
      # Cobb-Douglas
      cdModCSP <- 
        lm(log(eval(yVar)) - alphaCSP*log(eval(kVar)) - betaCSP*log(eval(lVar)) ~ eval(tVar), 
           data = data)
      # cdModCSP is an "lm" object. It is not a "CDEmodel" object. 
      # Thus, it needs its own "naturalCoeffs" attribute if it is to work correctly in the "naturalCoef" function.
      attr(cdModCSP, "naturalCoeffs") <- data.frame(lambda=coef(cdModCSP)[[2]],
                                                    logscale=coef(cdModCSP)[[1]], 
                                                    scale=exp(coef(cdModCSP)[[1]]),
                                                    alpha_1=alphaCSP,
                                                    alpha_2=betaCSP, 
                                                    alpha_3=0)
      cdModCSP$formula <- form
      sdata <- subset(data, select=all.vars(form))
      sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
      cdModCSP$data <- sdata
      cdModCSP$response <- sdata$iGDP
      modelsCSP[[country]][[adj]][["noE"]][["CD"]] <- cdModCSP
      # CES
      # The only CES models that can adhere to the CSP are models where
      # alpha values are constant with respect to time. 
      # I.e., models where energy is not included AND where rho_1 = 0.
      # CES models where rho_1 = 0 are the Cobb-Douglas model.
      # Convienently, we previously fit that model.
      cesModCSP <- cdModCSP
      # Again, we need a customized "naturalCoeffs" attribute so that 
      # the "naturalCoef" function will do the right thing.
      # "naturalCoeffs" can be based on the same "naturalCoeffs"
      # from the Cobb-Douglas model, but a few additions are needed.
      attr(cesModCSP, "naturalCoeffs") <- 
        naturalCoef(cdModCSP) %>%
        mutate(
          delta_1 = naturalCoef(cdModCSP)[["alpha_1"]],
          delta = 1,
          rho_1 = 0, 
          rho = NA
        )
      modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP
    }
  }
  # Save cost-share theorem models to disk.
  saveRDS(modelsCSP, file=fileNameCSP)

>>>>

  modelsCSP <- list()
  # Output elasticities based on cost share theorem
  alphaCSP <- 0.3 # Fraction of national accounts spent on capital
  betaCSP <- 0.7 # Fraction of national accounts spent on labor
  for (country in countries){
    for (adj in c("unadjusted", "adjusted")){
      # Replace with better code later. 
      # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
      # or something like that.
      form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
      yVar <- as.name(summands(form, n=1, right=FALSE))
      kVar <- as.name(summands(form, n=1))
      lVar <- as.name(summands(form, n=2))
      tVar <- as.name(summands(form, n=3))
      data <- historicalData[[country]]
      # Cobb-Douglas
      cdModCSP <- 
        lm(log(eval(yVar)) - alphaCSP*log(eval(kVar)) - betaCSP*log(eval(lVar)) ~ eval(tVar), 
           data = data)
      # cdModCSP is an "lm" object. It is not a "CDEmodel" object. 
      # Thus, it needs its own "naturalCoeffs" attribute if it is to work correctly in the "naturalCoef" function.
      attr(cdModCSP, "naturalCoeffs") <- data.frame(lambda=coef(cdModCSP)[[2]],
                                                    logscale=coef(cdModCSP)[[1]], 
                                                    scale=exp(coef(cdModCSP)[[1]]),
                                                    alpha_1=alphaCSP,
                                                    alpha_2=betaCSP, 
                                                    alpha_3=0)
      cdModCSP$formula <- form
      sdata <- subset(data, select=all.vars(form))
      sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
      cdModCSP$data <- sdata
      cdModCSP$response <- sdata$iGDP
      modelsCSP[[country]][[adj]][["noE"]][["CD"]] <- cdModCSP
      # CES
      # The only CES models that can adhere to the CSP are models where
      # alpha values are constant with respect to time. 
      # I.e., models where energy is not included AND where rho_1 = 0.
      # CES models where rho_1 = 0 are the Cobb-Douglas model.
      # Convienently, we previously fit that model.
      cesModCSP <- cdModCSP
      # Again, we need a customized "naturalCoeffs" attribute so that 
      # the "naturalCoef" function will do the right thing.
      # "naturalCoeffs" can be based on the same "naturalCoeffs"
      # from the Cobb-Douglas model, but a few additions are needed.
      attr(cesModCSP, "naturalCoeffs") <- 
        naturalCoef(cdModCSP) %>%
        mutate(
          delta_1 = naturalCoef(cdModCSP)[["alpha_1"]],
          delta = 1,
          rho_1 = 0, 
          rho = NA,
          sigma_1 = 1,
          sigma = NA
        )
      modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP
    }
  }
  # Save cost-share theorem models to disk.
  saveRDS(modelsCSP, file=fileNameCSP)
